Tor's Usability for Censorship Circumvention

### 2015-12-11 paper/circumvention-experiment.tex
Fix new typos

Many features of Tor that are left unevaluated through user
research --- such as advanced web tasks (e.g., accessing hidden services), the
configuration menu to connect to the Tor network, configuring automatic
updates, and identity/cookie management. Rather than selecting the features to
study in isolation, we decided to focus on an important use case of Tor browser: censorship circumvention. 
Internet censorship is pervasive across the world today \cite{faris2008measuring}. 
Although Tor was not designed to be a censorship circumvention tool, users started
using it as one, since Tor's role as a proxy to anonymize
people also worked to circumvent censorship. Now, circumventing censorship is a
common use case for Tor, and current censorship circumvention methods are
incorporated into Tor, making it a viable censorship circumvention tool even in the face
of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason \cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool.

@@

We collected feedback from researchers, professors, and Tor users and developers
through the Tor project's mailing lists. We iteratively designed by
incorporating the comments and suggestions we received into the next version of
the interface. We plan to take some qualitative measurements of the new design
by having some participants think aloud while they use our realistic mockup. This is 
to get any feedback before we launch our quantitative interface evaluation.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Challenge 1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen. As seen in Figure \ref{fig:window1}, there is some guidance for the users, but we found this largely unhelpful since people do not understand the text on the screen. 
\item {\bfseries Challenge 2:} People feel compelled to set up a bridge, even if they don't need one, because they do not know how censorship works. Participants knew that they were censored to some degree since we had simulated censorship of websites. However, bridges are only necessary when the government has taken active steps to censor Tor itself.
\item {\bfseries Challenge 3:} When their first attempt to connect fails, the interface directs people to the last window participants saw before the connection failure. The problem is not necessarily where the interface directs users, misguiding them. It was common for the interface to redirect users to the proxy window in Figure \ref{fig:window5}, even when they needed to pick another bridge. 
\item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next. The feedback given to users was not understood (see Figure \ref{fig:error}) and also did not guide users into specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
\end{itemize}

@@

A progress indicator at the top of indicates various steps
for configuring a connection. In addition to communicating what the various 
steps of configuration are from the beginning, this indicator also serves to clarify the independence of
bridges and proxies, which need to be configured separately.

@@

The progress bar in the connection window often was unresponsive 
and did not offer guidance for to wait. 
The connection process can take about two minutes long enough that users may
think that the connection has failed, even when it is making slow and invisible progress. 
We added a countdown timer to indicate that a long wait time does
not indicate failure. We also add visual indicators
for major milestones in the connection, providing better feedback about what has
been accomplished so far. Additionally, the current status of the connection
attempt (drawn from the log) is displayed, to aid in understanding and
debugging.

@@

\noindent {\bfseries Additional changes}
In addition to the changes above, we have simplified flows,
reduced text, and reduced visual clutter.
We believe these changes are cohesive with the our design 
and will be beneficial for the user.\\

>>>>

Many features of Tor have not been evaluated through user
research --- such as advanced web tasks (e.g., accessing hidden services), the
configuration menu to connect to the Tor network, configuring automatic
updates, and identity/cookie management. Rather than selecting the features to
study in isolation, we decided to focus on an important use case of Tor browser: censorship circumvention. 
Internet censorship is pervasive across the world today \cite{faris2008measuring}. 
Although Tor was not designed to be a censorship circumvention tool, users started
using it as one, since Tor's role as a proxy to anonymize
people also worked to circumvent censorship. Now, circumventing censorship is a
common use case for Tor, and current censorship circumvention methods are
incorporated into Tor, making it a viable censorship circumvention tool even in the face
of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason \cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool.

@@

We collected feedback from researchers, professors, and Tor users and developers
through the Tor project's mailing lists. We iteratively designed by
incorporating the comments and suggestions we received into the next version of
the interface. We plan to take qualitative measurements of the new design
by having participants think aloud while they use our realistic mockup. This is
to get any feedback before we launch our quantitative interface evaluation.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Challenge 1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen. As seen in Figure \ref{fig:window1}, there is some guidance for the users, but we found this largely unhelpful since people do not understand the text on the screen. 
\item {\bfseries Challenge 2:} People feel compelled to set up a bridge, even if they don't need one, because they do not know how censorship works. Participants knew that they were censored to some degree since we had simulated censorship of websites. However, bridges are only necessary when the government has taken active steps to censor Tor itself.
\item {\bfseries Challenge 3:} When their first attempt to connect fails, the interface directs people to the last window they saw before the connection failure. The problem is not necessarily where the interface directs users, misguiding them. It was common for the interface to redirect users to the proxy window in Figure \ref{fig:window5}, even when they needed to pick another bridge. 
\item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next. The feedback given to users was not understood (see Figure \ref{fig:error}) and also did not guide users into specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
\end{itemize}

@@

A progress indicator at the top of the window indicates various steps
for configuring a connection. In addition to communicating what the various 
steps of configuration are from the beginning, this indicator also serves to clarify the independence of
bridges and proxies, which need to be configured separately.

@@

The progress bar in the connection window was often unresponsive
and did not offer guidance for how long users were supposed to wait.
The connection process can take about two minutes --- long enough that users may
think that the connection has failed, even when it is making slow and invisible progress. 
We added a countdown timer to indicate that a long wait time does
not indicate failure. We also add visual indicators
for major milestones in the connection, providing better feedback about what has
been accomplished so far. Additionally, the current status of the connection
attempt (drawn from the log) is displayed, to aid in understanding and
debugging.

@@

\noindent {\bfseries Additional changes}
In addition to the changes above, we have simplified flows,
reduced text, and reduced visual clutter.
We believe these changes are cohesive with our design
and will be beneficial for the user.\\
